{fairmetrics}: An R package for group fairness evaluation

### 2025-06-05 utils/joss_paper/paper.Rmd
another fix

#>There is evidence that model does not satisfy equal opportunity.
#>  Metric GroupFemale GroupMale Difference    95% Diff CI Ratio 95% Ratio CI
#>1    FNR        0.38      0.62      -0.24 [-0.39, -0.09]  0.61 [0.44, 0.85]
```

>>>>

#> There is evidence that model does not satisfy equal opportunity.
#>   Metric GroupFemale GroupMale Difference    95% Diff CI Ratio 95% Ratio CI
#> 1    FNR        0.36      0.58      -0.22 [-0.37, -0.07]  0.62 [0.43, 0.89]
```
